Monte Carlo Corrections for Bayesian Methods

### 2017-05-17 papers/general_method/general.tex
Real

Unfortunately it is a rare scenario when dealing with nature and all her faults for us to be able to have a perfect step function or for selection efficiency to be wholly encapsulated by a single parameter. A more realistic scenario involves a selection efficiency which cannot be conveniently described by an analytic function and instead is a high dimensional non-analytic function. And its probably stochastic too, just to throw another wrench in the works.

>>>>

Unfortunately it is a rare scenario when dealing with nature and all her faults for us to have an analytic selection function. Let alone a function encapsulated by a single parameter. A more realistic scenario involves a selection efficiency which cannot be conveniently described by an analytic function. Instead, we would have a high dimensional non-analytic function. And its probably stochastic too, just to throw another wrench in the works.
